---
title: "VN e-commerce"
author: "NguyenLSCM"
output: 
               flexdashboard::flex_dashboard:
               theme: readable
---
<style>                     
.navbar {
  background-color:red;
  border-color:black;
}
.navbar-brand {
color:black!important;
}
</style>                    


```{r}
library(dygraphs)
library(dplyr)
library(lubridate)
library(scales)
library(xts)

```

```{r}

setwd("C:/Users/DellPC/Desktop")

tiki<-read.csv("tiki.csv")%>%mutate(name="tiki")%>% mutate(date=as.Date(date,format="%m/%d/%Y"))
sendo<-read.csv("sendo.csv")%>%mutate(name="sendo")%>% mutate(date=as.Date(date,format="%m/%d/%Y"))
shopee<-read.csv("shopee.csv")%>%mutate(name="shopee")%>% mutate(date=as.Date(date,format="%m/%d/%Y"))
lazada<-read.csv("lazada.csv")%>%mutate(name="lazada")%>% mutate(date=as.Date(date,format="%m/%d/%Y"))



tiki<-xts(x=tiki$n,order.by = as.Date(tiki$date))
sendo<-xts(x=sendo$n,order.by = as.Date(sendo$date))
lazada<-xts(x=lazada$n,order.by = as.Date(lazada$date))
shopee<-xts(x=shopee$n,order.by = as.Date(shopee$date))



dt<-cbind(tiki,sendo,shopee,lazada)



```

Ecommerce
=======================================

```{r}

dygraph(dt,main="The customer interation with 4 giant ecommerce company")%>%dyOptions(fillGraph = TRUE,pointShape = "star",drawPoints = TRUE,colors = c("darkorchid","red","green","blue"),gridLineColor = "black",drawGrid = TRUE,strokeBorderColor = "white",pointSize = 5)%>%dyHighlight(highlightCircleSize = 7,highlightSeriesBackgroundAlpha = 0.6,hideOnMouseOut = TRUE)%>%dyAxis(name="x",label="Giant Ecommerce Company")%>%dyAxis(name="y",label="Th number of searching times throughout time series")%>%dyLegend(show ="follow",hideOnMouseOut = FALSE)%>%  dyShading(from = "2017-08-31", to = "2017-09-30", color = "#FFE6E6") %>%
  dyShading(from = "2017-11-10", to = "2017-12-10", color = "#CCEBD6")%>%dySeries("tiki",label="TIKI")%>%dySeries("sendo",label="SENDO")%>%dySeries("lazada",label="LAZADA")%>%dySeries("shopee",label="SHOPEE")%>%dyRangeSelector(height=20)