---
title: "tiki_sendo_ecommerce"
author: "Nguyen_LSCM"
date: "3/25/2020"
output: html_document
---


![Tiki_Product](C:/Users/DellPC/Desktop/vnecommerce/Tiki_Product)
![Sendo_Product](C:/Users/DellPC/Desktop/vnecommerce/Sendo_Product)
![Tiki_Location](C:/Users/DellPC/Desktop/vnecommerce/Tiki_Location)
![Sendo_Location](C:/Users/DellPC/Desktop/vnecommerce/Sendo_Location)



```{r, warning=FALSE,message=FALSE,include=FALSE}

suppressMessages(library(tidyverse))
suppressMessages(library(plotly))
suppressMessages(library(stringr))
suppressMessages(library(stringi))
suppressMessages(library(lubridate))
suppressMessages(library(viridis))
suppressMessages(library(ggsci))
suppressMessages(library(patchwork))
suppressMessages(library(RColorBrewer))
theme_set(theme_minimal())

setwd("C:/Users/DellPC/Desktop/vnecommerce")

sendo<-read.csv("sendo.csv",header=TRUE)
tiki<- read.csv("tiki.csv",header=TRUE)

pal<-c(brewer.pal(8,"PRGn"),brewer.pal(8,"YlOrRd"),brewer.pal(8,"BrBG"))

sendo<-sendo%>% mutate(date=str_replace_all(date,pattern="T",replacement = " "))%>%mutate(date=as.POSIXct(date,format="%Y-%m-%d %H"))%>%mutate(hour=factor(hour(date)),weekday=factor(wday(date,abbr=TRUE,label=TRUE)))
tiki<-tiki%>% mutate(date=str_replace_all(date,pattern="T",replacement = " "))%>%mutate(date=as.POSIXct(date,format="%Y-%m-%d %H"))%>%mutate(hour=factor(hour(date)),weekday=factor(wday(date,abbr=TRUE,label=TRUE)))

gg1<-sendo%>% ggplot(aes(x=date,y=number))+geom_line(group=1,color="red",lwd=1)+xlab("Date")+ylab("Number of Searching for Sendo on google")+labs(title="The fluctuation of searching Sendo on Google")

gg2<- sendo%>%group_by(hour)%>%summarise(number=sum(number))%>%ggplot(aes(x=fct_reorder(hour,desc(number)),y=number,fill=hour))+geom_col()+coord_flip()+xlab("Hour of a day")+ylab("The Frequency in each hour")+labs("The plot of searching Sendo on Google in each hour")+scale_color_manual(values = pal)

gg3<- sendo%>%group_by(weekday)%>%summarise(number=sum(number))%>%ggplot(aes(x=fct_reorder(weekday,desc(number)),y=number,fill=weekday))+geom_col()+coord_flip()+xlab("weekday of a day")+ylab("The Frequency in each weekday")+labs("The plot of searching Sendo on Google in each weekday")+scale_fill_tron()

gg4<-sendo%>%group_by(weekday,hour)%>%summarise(number=sum(number))%>%ggplot(aes(x=hour,y=weekday,fill=number,label=number))+geom_tile()+scale_fill_viridis(option="D")+geom_label()+xlab("Hour")+ylab("Weekday")+labs(title = "Sendo, Hour versus Weekday")+geom_label(label.size = 3, fill="white")

gg5<-tiki%>%group_by(weekday,hour)%>%summarise(number=sum(number))%>%ggplot(aes(x=hour,y=weekday,fill=number,label=number))+geom_tile()+scale_fill_viridis(option="D")+geom_label()+xlab("Hour")+ylab("Weekday")+labs(title = "Tiki, Hour versus Weekday")+geom_label(label.size = 3, fill="white")

```



# Introduction

1. WHO
- Sendo and Tiki are  Vietnam start-up companieS in e-commerce. **But** THEY ARE VERY DIFFERENT FROM ``STRATEGY``.

<hr>

2. WHY

- `THE MAIN REASON`  IS *CUSTOMER SEGMENt*. 

<hr>

3. HOW TO PROVE 

               - Time to search on Google---> Time to work.
               - Location of customers ---> Where are customers from?
               - Range of product --> Price, Customer needed items?
               
<hr>



 **Sendo-Countryside and Tiki-City**
 
 

##Time to go shopping

```{r, warning=FALSE, message=FALSE,echo=FALSE,fig.align="left",fig.width=10,fig.height=10}

ggplotly(gg1)

```


```{r, warning=FALSE, message=FALSE,echo=FALSE,fig.align="left",fig.width=10,fig.height=10}

ggplotly(gg2)

```

```{r, warning=FALSE, message=FALSE,echo=FALSE,fig.align="left",fig.width=10,fig.height=10}
ggplotly(gg3)

```


```{r, warning=FALSE, message=FALSE,echo=FALSE,fig.align="left",fig.width=10,fig.height=10}
gg4
```

``````{r, warning=FALSE, message=FALSE,echo=FALSE,fig.align="left",fig.width=10,fig.height=10}

gg4/gg5

```


##Product



