---
title: "Data Crunching"
author: "Nguyen_LSCM"
date: "8/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries

```{r ,fig.height= 8, fig.width=10}

suppressMessages(library(tidyverse))
suppressMessages(library(reticulate))
suppressMessages(library(lubridate))
suppressMessages(library(readxl))
suppressMessages(library(plotly))
suppressMessages(library(leaflet))
suppressMessages(library(leafpop))
suppressMessages(library(patchwork))
suppressMessages(library(lubridate))

#set working directory

setwd('C:/Users/DellPC/Desktop/Corner/R_source_code/CEL/r1')

```

# Load datasets

```{r ,fig.height= 8, fig.width=10}

# Read the master dataset

customer <- read_excel('R1_CustomerMaster_Input.xlsx')
product  <- read_excel('R1_ProductMaster_Input.xlsx')

# Read so and to line dataset

soline <- read_excel('R1_SOLine_Input.xlsx')
toline <- read_excel('R1_TOLine_Input.xlsx')

```

Sort and filter for **customer dataset** dataset

```{r ,fig.height= 8, fig.width=10}

#Remove the replicate longitude and latitude

cusId <- customer %>% 
               add_count(Longitude, Latitude, sort = TRUE) %>% 
               filter(n<2) %>% 
               select(CusId)



customer %>% add_count(Longitude, Latitude, sort = TRUE) %>% 
               filter(n>1) %>%
               filter(CusId %in% cusId$CusId )



```

Sort and filter for **soline** dataset


```{r ,fig.height= 8, fig.width=10}

#Check for CusId, ProductId and Dateformat in Soline 

foo <- soline %>% filter(SoCustomerId %in% customer$CusId, SoProductId %in% product$ProductId) %>%
               mutate(SoEnteredDate = as.Date(SoEnteredDate, format = '%Y-%m-%d'),
                      SoExpectedDate = as.Date(SoExpectedDate, format = '%Y-%m-%d'))

soline <- foo

#Check for 

foo <- toline %>% filter(ToCustomerId %in% customer$CusId, ToProductId %in% product$ProductId,
                         SoOrderLineId %in% soline$SoOrderLineId) %>% 
                  mutate(ToDeparturedDate = as.Date(ToDepartureDate, format = '%Y-%m-%d'),
                      ToArrivalDate = as.Date(ToArrivalDate, format = '%Y-%m-%d'))

toline <- foo


```

# Shipment by Customer Result

```{r ,fig.height= 8, fig.width=10}

cus_so <- customer %>% select(CusId) %>% 
               left_join(soline, by = c('CusId' = 'SoCustomerId')) %>% 
               na.omit() %>%
               group_by(CusId) %>% 
               summarise(TotalOrderedQuantityKg = sum(SoQuantity),
                         NumberOfOrderNumber = n()
                         ) %>%
               mutate(AverageQuantityPerOrderKg = TotalOrderedQuantityKg / NumberOfOrderNumber)

so_price <- soline %>% 
               group_by(SoProductId) %>% 
               summarise(price = mean(SoUnitCost))


cus_to <- customer %>% select(CusId) %>%
               left_join(toline, 
                         by =c('CusId' = 'ToCustomerId')) %>%
               na.omit() %>% 
               left_join(so_price, 
                         by =c('ToProductId' ='SoProductId')) %>%
               mutate(SalesValue = price*ToQuantity) %>%
               group_by(CusId) %>% 
               summarise(TotalShippedQuantityKg = sum(ToQuantity),
                         SalesValue = sum(SalesValue))

cus_so_to <- cus_so %>% 
               left_join(cus_to, by = 'CusId') %>% 
               arrange(desc(SalesValue)) %>% 
               mutate(CumulativeValueSharePercent = cumsum(SalesValue/ sum(SalesValue)),
                      OrderFillRatePercent = TotalShippedQuantityKg/TotalOrderedQuantityKg) %>%
               mutate(AbcClass = if_else(CumulativeValueSharePercent < 0.8, 'A',
                                         if_else(CumulativeValueSharePercent > 0.95, 'C', 'B')))



```

# Shipment by Productgroup Result

```{r ,fig.height= 8, fig.width=10}

product_so <- product %>% select(ProductGroup, ProductId) %>% 
               left_join(soline, by = c('ProductId' = 'SoProductId')) %>% 
               na.omit() %>%
               group_by(ProductGroup, ProductId) %>% 
               summarise(TotalOrderedQuantityKg = sum(SoQuantity)) %>% ungroup() %>%
               group_by(ProductGroup) %>% 
               summarise(TotalOrderedQuantityKg = sum(TotalOrderedQuantityKg))
                     

so_price <- soline %>% 
               group_by(SoProductId) %>% 
               summarise(price = mean(SoUnitCost))

product_to <- product %>% select(ProductGroup, ProductId) %>%
               left_join(toline, 
                         by =c('ProductId' = 'ToProductId')) %>%
               na.omit() %>% 
               left_join(so_price, 
                         by =c('ProductId' ='SoProductId')) %>%
               mutate(SalesValue = price*ToQuantity) %>%
               group_by(ProductGroup, ProductId) %>% 
               summarise(TotalShippedQuantityKg = sum(ToQuantity),
                         SalesValue = sum(SalesValue)) %>% ungroup() %>%
               group_by(ProductGroup) %>%
               summarise(TotalShippedQuantityKg = sum(TotalShippedQuantityKg),
                         SalesValue = sum(SalesValue))

product_so_to <- product_so %>% 
               left_join(product_to, by = 'ProductGroup') %>% 
               mutate(OrderFillRatePercent = TotalShippedQuantityKg/TotalOrderedQuantityKg) 
```

# Transaction Summary Result

```{r ,fig.height= 8, fig.width=10}

df <- soline %>% select(SoProductId, SoQuantity, SoUnitCost) %>%
               left_join(product %>% select(ProductId, KgPerCarton),
                         by =c('SoProductId' = 'ProductId')) %>% 
               select(SoProductId, KgPerCarton)

so_summary <- soline %>% select(SoProductId, SoQuantity, SoUnitCost) %>%
               left_join(df, by = c('SoProductId')) %>%
               transmute(SoProductId = SoProductId,
                         TotalValue = SoQuantity*SoUnitCost,
                         QuantityCar = SoQuantity/KgPerCarton,
                         SoQuantity = SoQuantity) %>%
               group_by(SoProductId) %>%
               summarise(SoQuantity = sum(SoQuantity), 
                         TotalValue = sum(TotalValue),
                         QuantityCar = sum(QuantityCar)) %>%
               mutate( Summary = 'Sales Order') %>%
               group_by(Summary) %>% 
               summarise(WeightTon = sum(SoQuantity)/1000, 
                         TotalValue = sum(TotalValue),
                         QuantityCar = sum(QuantityCar))



df <- toline %>% select(ToProductId, ToQuantity) %>%
               left_join(product %>% select(ProductId, KgPerCarton),
                         by =c('ToProductId' = 'ProductId')) %>% 
               select(ToProductId, KgPerCarton) %>%
               left_join(soline %>% select(SoProductId, SoUnitCost), 
                         by = c('ToProductId' = 'SoProductId'))  %>%
               group_by(ToProductId) %>%
               summarise(KgPerCarton = mean(KgPerCarton),
                         SoUnitCost = mean(SoUnitCost))

to_summary <- toline %>% select(ToProductId, ToQuantity) %>%
               left_join(df, by = c('ToProductId')) %>%
               transmute(ToProductId = ToProductId,
                         TotalValue = ToQuantity*SoUnitCost,
                         QuantityCar = ToQuantity/KgPerCarton,
                         ToQuantity = ToQuantity) %>%
               group_by(ToProductId) %>%
               summarise(ToQuantity = sum(ToQuantity), 
                         TotalValue = sum(TotalValue),
                         QuantityCar = sum(QuantityCar)) %>%
               mutate( Summary = 'Transportation Order') %>%
               group_by(Summary) %>% 
               summarise(WeightTon = sum(ToQuantity)/1000, 
                         TotalValue = sum(TotalValue),
                         QuantityCar = sum(QuantityCar))

transaction_summary <- bind_rows(so_summary, to_summary)


```

# Export files

```{r ,fig.height= 8, fig.width=10}

write_csv(customer, path = 'template/customer_master_result.csv')
write_csv(product, path = 'template/product_master_result.csv' )
write_csv(soline, path = 'template/sales_order_result.csv')
write_csv(toline, path = 'template/transportation_order_result.csv')

write_csv(cus_so_to, path = 'template/shipment_by_customer_result.csv')
write_csv(product_so_to, path = 'template/shipment_by_productgroup_result.csv')
write_csv(transaction_summary, path = 'transaction_summary_result.csv')

```


# Mine the Customer Master dataset

```{r ,fig.height= 8, fig.width=10}

library(leaflet)

customer %>% leaflet() %>% 
               addTiles() %>% addProviderTiles(provider = providers$OpenStreetMap.DE) %>%
               addProviderTiles((provider = providers$TomTom.Labels)) %>%
               addCircleMarkers(lng = ~Longitude, lat =~ Latitude, label = ~CusId, color = 'darkred')



```

# Mine the Product Master dataset

```{r ,fig.height= 8, fig.width=10}

gg <- ggplot(data =  product, aes(y = fct_reorder(Name, -KgPerCarton))) +
               geom_bar(stat='identity', aes(x= KgPerCarton ,fill = ProductGroup))  + 
               geom_text(data = product, aes(x = KgPerCarton/2, label = KgPerCarton), 
                         color ='white', fontface = 'bold' ) +
               labs(title = 'KgPerPallet for each Product', x = 'Product Group', y ='KgPerCaton') +
               scale_fill_manual(values = c('red', 'steelblue', 'green')) +
               theme_bw()

ggplotly(gg)

```


```{r ,fig.height= 8, fig.width=10}
library(reticulate)

```

```{python}

import plotly.express as px
import plotly.graph_objs as go
import plotly.offline as pyo

```

```{python, fig.height= 8, fig.width=10}

df = r.product

fig = px.sunburst(df, path = ['ProductGroup', 'Name'], values = 'KgPerCarton',
                  color=df['KgPerCarton'],
                  color_continuous_scale = 'orrd')
                  

fig.update_layout(title = 'Product Summary', title_x = 0.5)

pyo.plot(fig, filename='Product_summary.html', auto_open=False)

```




```{r ,fig.height= 8, fig.width=10}

htmltools::includeHTML('Product_summary.html')

```



# So order mining


```{python}

# Import modules 

import numpy as np
import pandas as pd 

from datetime import datetime


import requests
import folium
from folium.plugins import FastMarkerCluster, Fullscreen, MiniMap, HeatMap, HeatMapWithTime, LocateControl

# Draw the time frame heatmap with number of SolineId

df = r.soline
dt = r.customer

df = df.merge(dt[['CusId', 'Longitude', 'Latitude']], how = 'left', right_on ='CusId', left_on = 'SoCustomerId')

df['SoEnteredDate'] = pd.to_datetime(df['SoEnteredDate'])
df['SoExpectedDate'] = pd.to_datetime(df['SoExpectedDate'])
df['month'] = df['SoEnteredDate'].apply(lambda x: x.month)
df['dayofweek'] = df['SoEnteredDate'].apply(lambda x: x.dayofweek)
df['year_month'] = df['SoEnteredDate'].apply(lambda x: x.strftime('%Y%m'))


# Draw the maps 

epoch_list = []


time_index = df['year_month'].sort_values().unique()

for epoch in time_index:
    data_temp = df.query('year_month == @epoch')
    data_temp = data_temp.groupby(by=['Longitude', 'Latitude'], as_index = False).count()
    data_temp = data_temp.sort_values(by = 'SoOrderId', ascending = False).iloc[:, :3]
    epoch_list.append(data_temp.values.tolist())
    
    
map2 = folium.Map(location = [-72, -15],
                 zoom_start = 4.0,
                 tiles = 'cartodbdark_matter')

# Plugin:HeatMapWithTime

HeatMapWithTime(
    name = 'Evolution of Orders in a Geolocation Perspective',
    data =epoch_list,
    radius = 10, 
    index = list(time_index)
    ).add_to(map2)

map2.save('time_frame_customer_map.html')
    
    
```


```{r}

htmltools::includeHTML('time_frame_customer_map.html')

```


## SalesOrder of Customer through 5 months 

```{r, fig.height= 12, fig.width=8}

foo <- soline %>% mutate(SalesValue = SoQuantity*SoUnitCost, month = month(SoEnteredDate)) 

df <- foo %>% group_by(SoCustomerId) %>%
               summarise(SalesValue = sum(SalesValue)/5) %>% 
               arrange(desc(SalesValue)) %>%
               head(20)

foo %>% filter(SoCustomerId %in% df$SoCustomerId) %>%
               group_by(SoCustomerId, month) %>% 
               summarise(SalesValue = sum(SalesValue)) %>%
               arrange(desc(SalesValue)) %>%
               ggplot(aes(x = month, y = SalesValue, color = SoCustomerId)) + 
               geom_line(aes(group = 1), show.legend = FALSE, lwd =1) + 
               coord_polar()+
               facet_wrap(~SoCustomerId, nrow = 4, ncol = 5) +
               labs(title = 'SalesValue of each Customer in each Month', x = 'Date', y = 'SalesValue') +
               theme_light()


```




# Customer summary mining

```{r ,fig.height= 8, fig.width=10}

map_df <- cus_so_to %>% select(CusId, SalesValue, 
                               OrderFillRatePercent, AbcClass) %>%
               left_join(customer %>% 
                                        select(CusId, Longitude, Latitude), by = 'CusId') 


pal<-colorFactor(c('red', 'steelblue', 'palegreen'),domain = c("A","B","C"))

map_df %>% leaflet() %>% addTiles() %>% 
               addProviderTiles(provider = providers$OpenStreetMap) %>%
               addProviderTiles(provider = providers$Stamen.TonerLabels) %>% 
               addCircleMarkers(data =map_df ,lng = ~Longitude, lat = ~Latitude,
                                                         color = ~pal(AbcClass),
                                                         fillOpacity = 0.5,
                                                         popup =  leafpop::popupTable(map_df,
                                              feature.id = FALSE,
                                              row.numbers = FALSE,
                                              zcol=c('SalesValue', 'OrderFillRatePercent', 'AbcClass')),
                                                         radius = ~log(SalesValue))

```


# ProductGroup summary mining

```{r ,fig.height= 8, fig.width=10}

product_df <- product_so_to %>% pivot_longer(cols = c('TotalOrderedQuantityKg', 'TotalShippedQuantityKg'),
                                              names_to = 'ordered_shipped',
                                             values_to = 'quantity')

p1 <- product_df %>% ggplot(aes(x = ProductGroup)) + 
               geom_bar(data = product_df, aes(y = SalesValue, fill = ProductGroup),
                        stat = 'identity', show.legend = FALSE) + 
               labs(title = 'Sales Value for each Product group',
                    x = 'Product Group', y ='Sales Value') +
               theme_light()
           

p1
  

p2 <-   product_so_to %>% ggplot(aes(x = ProductGroup, y = OrderFillRatePercent)) + 
               geom_line(aes(group = 1), lwd =2, color = 'cyan4') + 
               geom_point(aes(color = ProductGroup), size = 8)+
               labs(title = 'OrderFillRatePercent for each Product Group', 
                    x = ' ProductGroup' , y ='OrderFillRatePercent') +
               coord_polar() + theme_light()


p2
             

p3 <-  product_df %>% ggplot(aes(x = ProductGroup, label = quantity)) + 
               geom_bar(data = product_df, aes(y = quantity, fill = ordered_shipped),
                        stat = 'identity', position = 'dodge', alpha = 0.8) +
               labs(title = 'Ordered and Shipped Quantity for each Product group  ',
                    x = 'Product Group', y ='Sales Value', legend = F) +
               scale_fill_manual(values = c('darkred', 'lightgreen')) +
               theme_light()

p3

layout = 'AB
          CC'

p1 + p2 +p3 + plot_layout(design = layout)
               
```

